The data conained in challenger.csv are the launch temperatures (degrees Farenheit) and an indicator of O-ring failures for 24 space shuttle launches prior to the space shuttle Challenger disaster of January 28, 1986.

```{r}
# import dataset
challenger <- read_csv('C://Users/cgada/OneDrive/Documents/datasets/challenger.csv')

head(challenger)
```

## Fitting the logistic regression of Failure (1 for failure) on Temperaure, and reporting the estimated coefficients and their standard errors.

```{r}
# converting failure into binary
challenger$Failure <- if_else(challenger$Failure == 'Yes', 1, 0)

# creating logistic regression model
challengerglm <- glm(Failure ~ Temperature, data = challenger, family = binomial)

# summary of model
challengerglm %>% summary() %>% pander()

```

The estimated coefficients and their corresponding standard errors can be located in the summary table above.

Testing whether the coefficient of Temperature is 0, using Walds test, and reporting a one-sided p-value (the alternative hypothesis is that the coefficient is negative; odds of failure decrease with increasing temperature).

```{r}
# betahat established
betahat <- coef(challengerglm)

# wald test
wald.test(Sigma = vcov(challengerglm), b = betahat, Terms = 2)

```

* P-value = 0.04

## Now testing whether the coefficient of Temperature is 0, using the drop-in-deviance test.

```{r}
# first making null
challengerlogitnull <- glm(Failure ~ 1, data = challenger, family = binomial)

# anova
anova(challengerlogitnull, challengerglm, test = "LRT")

```

The outcome of our likelihood ratio tests suggests that the coefficient of Temperature is statistically different from 0.

## 95% confidence interval for the coefficient of Temperature.

``{r}
# default CI function
CI_95 <- confint.default(challengerglm)
CI_95 %>% summary() %>% pander()
```

## Estimated logit of failure probability at 31 degrees, and estimated probability of failure?

```{r}
# logit
challengerlogit <- glm(Failure ~ Temperature, data = challenger, family = binomial)

# prediction
predict(challengerlogit, newdata = data.frame(Temperature = 31), type = "response")
```

The probability of failure at 31 degrees Fahrenheit (the temperature at which Challenger was actually launched at) is **99.62%**. This means that they probably should not have launched. Politics...

This answer must be treated cautiously because lives are at stake, tax-payers dollars are at stake, and jobs are at stake. The launch should not have been rushed simply because it was already pushed back and they wanted to keep to a schedule. If there is a chance of failure like that, it should not be taken.


